Code for Submission

### 2023-08-08 CodeForSubmission.Rmd
Changes for next round of revisions (in response to reviewer comments and Joel feedback).

```{r}
data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
data <- data[complete.cases(data[, 1]), ]
data$fate <- factor(data$fate, levels = c("wander", "em", "wowe", "wowe mongo"))

@@

```{r}
datadead <- datadead[datadead$fate != "quink" & datadead$fate != "wander*" & datadead$fate != "?", ]
datadead <- datadead[complete.cases(datadead[, 1]), ]
datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
```

@@

### a. Figure 1

```{r}
data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))

dataviolin <- data
#dataviolin$fate <- gsub(" mongo", "", dataviolin$fate)
#dataviolin$fate <- factor(dataviolin$fate, levels = c("wander", "em", "wowe"))
```

```{r}
violins <- ggplot(data = dataviolin, aes(x = treatment, y = mass.max/1000)) + 
  geom_violin(fill = "light grey", color = "light grey") + 
  geom_jitter(aes(color = fate, shape = food), width = 0.1, height = 0) + 
  theme_bw() + 
  labs(x = "Treatment Group", y  = "Maximum mass achieved (g)",  color = "System Outcome", shape = "Hostplant") + 
  scale_color_manual(values = c("wander" = "#1E88E5" , "em" = "lime green", 
                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
                    labels = c("Caterpillar pre-pupation", "Wasp emergence", 
                               "Wasp larval death", "Wasp egg death")) +
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco"))

violins
```

*Brackets and text annotated in Photoshop*

@@

```{r}
datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
datadead$fate <- factor(datadead$fate, levels = c("dead", "wander", "em", "wowe", "wowe mongo"))
```

@@

```{r}
barsdead <- ggplot(data = datadead, aes(x = treatment, fill = fate)) + 
  theme_bw() + 
  geom_bar(position = "fill") + 
  facet_wrap(~food) + 
  scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "System Outcome") + 
  scale_fill_manual(values = c("dead" = "purple", "wander" = "#1E88E5" , "em" = "lime green", 
                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
                    labels = c("Died before expt. end", "Caterpillar pre-pupation", "Wasp emergence", 
                               "Wasp larval death", "Wasp egg death")) + 
  geom_text(data = samplesize, aes(x = x, y = y, label = N))

@@

@@

```{r}
datamulti <- data[data$para == "yes" & data$HS == "yes", ]
datamulti$fate <- factor(datamulti$fate, levels = c("em", "wander", "wowe", "wowe mongo"), labels = c("WE", "Wander", "Small WOWE", "Large WOWE"))
datamulti$food <- factor(datamulti$food, levels = c("TB", "DC"))
```

@@

```{r}
newmeans <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
  theme_bw() + 
  xlim(15, 45) +
  geom_point(alpha = 0.4) + 
  scale_shape_manual(values = c(1, 19)) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
                     labels = c("Wander", "WE", "Small WOWE", "Large WOWE")) + 
  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
  guides(size = FALSE) + 
  labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Hostplant Consumed", color = "Developmental Outcome")

newmeans
```

```{r}
datalong5$treatment <- factor(datalong5$treatment, labels = c("Non-parasitized non-heat shocked", "Non-parasitized heat shocked", "Parasitized non-heat shocked", "Parasitized heat shocked"))

newmeansfacet <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
  facet_wrap(~ treatment) + 
  theme_bw() + 
  xlim(15, 45) +
  ylim(0, 20) + 
  geom_point(alpha = 0.8) + 
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco")) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
                     labels = c("Caterpillar pre-pupation", "Wasp emergence", "Wasp larval death", 
                                "Wasp egg death")) + 
#  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
#  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
#  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
#  guides(size = FALSE) + 
  labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Hostplant", color = "System Outcome")

@@

@@

```{r}
newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
  theme_bw() + 
  geom_point(alpha = 0.4) + 
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacaco")) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
                     labels = c("Caterpillar pre-pupation", "Wasp emergence", "Wasp larval death", 
                                "Wasp egg death")) + 
  ylim(0, 20) + 
  xlim(0, .6) +
  geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5, width = 0) + 
  geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
  guides(size = FALSE) + 
  labs(x = expression(paste("Hostplant leaf area consumed ", (m^{2}))), y = "Maximum mass achieved (g)", 
       shape = "Hostplant", color = "System Outcome")

@@

>>>>

```{r}
data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
data <- data[complete.cases(data[, 1]), ]
data$fate <- gsub("wowe mongo", "wowe", data$fate)
data$fate <- factor(data$fate, levels = c("wander", "em", "wowe"))

@@

```{r}
datadead <- datadead[datadead$fate != "quink" & datadead$fate != "wander*" & datadead$fate != "?", ]
datadead <- datadead[complete.cases(datadead[, 1]), ]
datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
datadead$fate <- gsub("wowe mongo", "wowe", datadead$fate)
```

@@

@@

```{r}
datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
datadead$fate <- factor(datadead$fate, levels = c("dead", "wander", "em", "wowe"))
datadead$food <- factor(datadead$food, levels = c("DC", "TB"), labels = c("Devil's claw", "Tobacco"))
```

@@

```{r}
barsdead <- ggplot(data = datadead, aes(x = treatment, fill = fate)) + 
  theme_bw() + 
  geom_bar(position = "fill") + 
  facet_wrap(~food) + 
  scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
  scale_fill_manual(values = c("dead" = "purple", "wander" = "#1E88E5" , "em" = "lime green", 
                                       "wowe" =  "#D81B60"),
                    labels = c("Died before expt. end", "Wandering", "Wasp emergence", 
                               "Without wasp emergence")) + 
  geom_text(data = samplesize, aes(x = x, y = y, label = N))

@@

```{r}
ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/Fig2new.png", barsdead, width = 8, height = 5)
```

@@

```{r}
datamulti <- data[data$para == "yes" & data$HS == "yes", ]
datamulti$fate <- factor(datamulti$fate, levels = c("em", "wander", "wowe"), labels = c("WE", "Wander", "WOWE"))
datamulti$food <- factor(datamulti$food, levels = c("TB", "DC"))
```

@@

```{r}
datalong5$treatment <- factor(datalong5$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"), labels = c("Non-parasitized non-heat shocked", "Non-parasitized heat shocked", "Parasitized non-heat shocked", "Parasitized heat shocked"))

newmeansfacet <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
  facet_wrap(~ treatment) + 
  theme_bw() + 
  xlim(15, 45) +
  ylim(0, 20) + 
  geom_point(alpha = 0.8) + 
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco")) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
                     labels = c("Wandering", "Wasp emergence", "Without wasp emergence")) + 
#  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
#  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
#  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
#  guides(size = FALSE) + 
  labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Hostplant", color = "Developmental Outcome")

@@

```{r}
ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/Fig4new.png", newmeansfacet, width = 8, height = 5)
```

@@

```{r}
newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
  theme_bw() + 
  geom_point(alpha = 0.8, size = 2.5) + 
  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacaco")) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
                     labels = c("Wandering", "Wasp emergence", "Without wasp emergence")) + 
  ylim(0, 20) + 
  xlim(0, .6) +
 # geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
 # geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5, width = 0) + 
 # geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
  guides(size = FALSE) + 
  labs(x = expression(paste("Hostplant leaf area consumed ", (m^{2}))), y = "Maximum mass achieved (g)", 
       shape = "Hostplant", color = "Developmental Outcome")

@@

```{r}
ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/Fig5new.png", newarea, width = 8, height = 5)
```
